Reintroduction of resistant frogs facilitates landscape-scale recovery in the presence of a lethal fungal disease

### 2024-04-05 doc/manuscript/translocation.qmd
Update Figure S5 legend

![Sensitivity analysis of the stage-structured MYL frog model. Elasticity of $\lambda$ with changes in six parameters: $\sigma_{A_R}$ (yearly survival probability of naturally recruited adults), $F$ (number of eggs produced by a female frog in a year that successfully hatch), $\sigma_{J_1}$ (yearly probability of survival of year-1 juveniles that also affects recruitment), $\sigma_{J_2}$ (yearly probability of survival and recruitment of year-2 juveniles), $p_{L_2}$ (probability that year 2 tadpoles metamorph into juveniles), $p_{J_1}$ (probability that year 1 juveniles mature to adults). We did not include $p_{L_1}$ as this parameter is generally 1 across populations (Table S1) -- tadpoles must spend at least a year as tadpoles before metamorphosing. Elasticity is calculated at the default parameter values for each population and $\sigma_{J_1}$ = 0.09.](figures/pop_viability_figures_for_supp.jpg){#fig-viability-supp width="550"}

>>>>

![Sensitivity analysis of the stage-structured MYL frog model. Elasticity of $\lambda$ with changes in six parameters: $\sigma_{A_R}$ (yearly survival probability of naturally recruited adults), $F$ (number of eggs produced by a female frog in a year that successfully hatch), $\sigma_{J_1}$ (yearly probability of survival of year-1 juveniles that also affects recruitment), $\sigma_{J_2}$ (yearly probability of survival and recruitment of year-2 juveniles), $p_{L_2}$ (probability that year 2 tadpoles metamorph into juveniles), $p_{J_1}$ (probability that year 1 juveniles mature to adults). We did not include $p_{L_1}$ as this parameter is generally 1 across the populations in this study populations (Table S1) -- tadpoles must spend at least a year as tadpoles before metamorphosing. Elasticity is calculated at the default parameter values for each population and $\sigma_{J_1}$ = 0.09.](figures/pop_viability_figures_for_supp.jpg){#fig-viability-supp width="550"}
